-

### 2023-01-17 DRAFT_homogeneous_impact_areas.Rmd
doc: Why aggregate

## Discretize the entire map

##

>>>>

## Discretize the entire map
```{r}
names(infra) <- "infrastructureIndex"

infra_discrete <- infra %>%
  mutate(infrastructureIndex = case_when(
    infrastructureIndex < 1 ~ 0,
    infrastructureIndex < 6 ~ 1,
    infrastructureIndex < 9 ~ 2,
    infrastructureIndex >= 9 ~ 3
  ))
```

## Aggregate
The resolution in this map is more than we need, and the size of the data implies that the next step, the vectorization, would take too long.
We therefore aggregate, ar reduce the resolution.
